Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-10-31 paper/paper.qmd
Update script

```{r}
#| label: fig-pct
#| fig-cap: Distribution of Support (percent) for Donald Trump
#| echo: false
#| warning: false
#| message: false
ggplot(analysis_data, aes(x = percent)) +
  geom_histogram(binwidth = 2, fill = "green", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Support (percent) for Donald Trump", x = "Support Percentage (percent)", y = "Count") +
  theme_minimal()
```

@@

ggplot(analysis_data %>% distinct(pollster_rating_name, .keep_all = TRUE), 
       aes(x = numeric_grade)) + 
    geom_histogram(binwidth = 0.1, fill = "green", color = "black", alpha = 0.7) + 
    scale_x_continuous(breaks = seq(2.5, 3.0, by = 0.1)) + 
    scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) + 
    labs(title = "Distribution of Numeric Grades (2.6 to 3.0)", 
         x = "Numeric Grade", 
         y = "Count of Distinct Polls") + 
    theme_minimal()
```
### Sample Size

@@

ggplot(analysis_data %>% filter(sample_size < 3000), aes(x = sample_size)) +
  geom_histogram(binwidth = 100, fill = "green", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Sample Size", x = "Sample Size", y = "Count") +
  theme_minimal()
```
### Transparency Score

@@

ggplot(analysis_data %>% 
         distinct(pollster_rating_name, .keep_all = TRUE), 
       aes(x = transparency_score)) + 
  geom_histogram(binwidth = 1, fill = "green", color = "black", alpha = 0.7) + 
  scale_x_continuous(breaks = 3:10) +
  scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) +  
  labs(title = "Distribution of Transparency Score", x = "Transparency Score", y = "Count of Distinct Polls") + 
  theme_minimal()
```

@@

ggplot(analysis_data, aes(x = as.Date(end_date))) + 
  geom_line(stat = "count", color = "black", size = 1) + 
  labs(title = "Distribution of End Dates", x = "End Date", y = "Count") + 
  theme_minimal()

>>>>

```{r}
#| label: fig-pct
#| fig-cap: Distribution of Support (percent) for Donald Trump
#| echo: false
#| warning: false
#| message: false
ggplot(analysis_data, aes(x = percent)) +
  geom_histogram(binwidth = 2, fill = "pink", color = "white", alpha = 0.7) +
  labs(title = "Distribution of Support (percent) for Donald Trump", x = "Support Percentage (percent)", y = "Count") +
  theme_minimal()
```

@@

ggplot(analysis_data %>% distinct(pollster_rating_name, .keep_all = TRUE), 
       aes(x = numeric_grade)) + 
    geom_histogram(binwidth = 0.1, fill = "pink", color = "white", alpha = 0.7) + 
    scale_x_continuous(breaks = seq(2.5, 3.0, by = 0.1)) + 
    scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) + 
    labs(title = "Distribution of Numeric Grades (2.6 to 3.0)", 
         x = "Numeric Grade", 
         y = "Count of Distinct Polls") + 
    theme_minimal()
```
### Sample Size

@@

ggplot(analysis_data %>% filter(sample_size < 3000), aes(x = sample_size)) +
  geom_histogram(binwidth = 100, fill = "pink", color = "white", alpha = 0.7) +
  labs(title = "Distribution of Sample Size", x = "Sample Size", y = "Count") +
  theme_minimal()
```
### Transparency Score

@@

ggplot(analysis_data %>% 
         distinct(pollster_rating_name, .keep_all = TRUE), 
       aes(x = transparency_score)) + 
  geom_histogram(binwidth = 1, fill = "pink", color = "white", alpha = 0.7) + 
  scale_x_continuous(breaks = 3:10) +
  scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) +  
  labs(title = "Distribution of Transparency Score", x = "Transparency Score", y = "Count of Distinct Polls") + 
  theme_minimal()
```

@@

ggplot(analysis_data, aes(x = as.Date(end_date))) + 
  geom_line(stat = "count", color = "pink", size = 1) + 
  labs(title = "Distribution of End Dates", x = "End Date", y = "Count") + 
  theme_minimal()
